Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-16 paper/reviewers-response.Rmd

> "In the literature on ecological networks, the term keystone species has often been tossed around without any clear definition. I was pleased to read that here the authors have developed a cleaner, more effective way to identify keystone species in ecological networks than methods that have been proposed before. I think the authors have made the correct choice in emphasizing the conceptual aspects of the approach, and do so quite well. The background on control theory was complex but manageable to read and understand in this context."

We are very thankful for the positive feedback.

> "Overall I found the paper well-written and sound, but there were a few questions I had that could improve clarity in the methods used. In the glm that used nD as the response variable, is there any concern that including N (number of species) as a predictor may cause a problem when the response is D/N? I can understand why this was included, but I can also imagine this resulting in models that show an effect of N when there is none (I could be wrong on this)."

Thanks for the observation. As you mention, we believe it is ok to include the sample size as a predictor in this model for three reasons. First, there are several instances when the probability of something occurring increases or decreases with sampling size, sampling effort, etc. A common ecological example would be a saturating predator functional response. Though this implies an underlying *non-linear* relationship, it does not invalidate the approach. Second, if there were a relationship between N and D, using D/N as the response variable (as opposed to D) and N as a predictor should actually reduce the size of the inferred effect of N, rather than amplify it. On the other hand, if N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of N. Third, in our manuscript we found a comparatively small effect of N on D. Although it might be relevant statistically, it seems to be ecologically insignificant.

### 2019-01-17 paper/reviewers-response.Rmd

---
title: "Keystoneness, centrality, and the structural controllability of ecological networks"
subtitle: "JEcol-2018-0545.R1 - Detailed response to comments"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \usepackage{lineno}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}
  - \externaldocument[S-]{supp-info}
  - \usepackage[most]{tcolorbox}
  - \definecolor{block-gray}{gray}{0.9}
  - \newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}
---

@@

\renewcommand\thefigure{R\arabic{figure}}    
\setcounter{figure}{0}

\doublespacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

We are thankful to the assistant editor James Ross, the senior editor and David Gibson, and three anonymous reviewers for the insightful comments to improve the manuscript. 
In the following sections, you can find a detailed response to each comment raised in this round of review.

### 2019-02-18 paper/manuscript.Rmd
Remove "keystone species" from keywords
Only 8 keywords are allowed. Removed because it already appears a couple of times in the abstract

**Keywords:** Invasive species, keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability

>>>>

**Keywords:** Invasive species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability
